### 2019-08-06 1_introduction.tex
Tweak.

We conduct a comprehensive comparative study of Task Bench
implementations in 15 programming systems:
Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP and CUDA),
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG, we find a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While in the most simplified scenarios, some systems can
achieve a METG(50\%) of 390~ns, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies. We find asynchronous systems provide benefits
(e.g., overlapping compute and communication), but only if system overheads do not exceed roughly
100~\textmu{}s.

>>>>

We conduct a comprehensive comparative study of Task Bench
implementations in 15 programming systems:
Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask15}, MPI \cite{MPI}, MPI+X (OpenMP and CUDA),
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG, we find a number of factors---node
count, accelerators, and complex dependencies, among
others---individually or in combination contribute to an order of
magnitude or greater increase in METG, even in the most efficient
systems. While in the most simplified scenarios, some systems can
achieve a METG(50\%) of 390~ns, we show that a more realistic
bound for running nearly any application at scale is 100~\textmu{}s with
current technologies. We find asynchronous systems can provide benefits
(e.g., overlapping compute and communication), but only if system overheads do not exceed roughly
100~\textmu{}s.
